The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Edits to nu section of paper

We now describe the options available for the function {\tt nu}.  We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when the second input is instead a polynomial $f$.

In general, the function {\tt nu} works by searching through the list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
The user can specify how this search is approached through the  option {\tt Search}.  Namely, a binary search is used when {\tt Search} is set to {\tt Binary} (and this is the option's default value), and a linear search is run when it is set to {\tt Linear}.

@@

As described in the introduction, the integer $\nu_I^J(p^e)$ is defined in terms of the containment conditions on powers of ideals.
For positive integers $n$ and $e$, and an ideal $I$ contained in the radical of another ideal $J$, we have that
\begin{equation*}
  I^n \subseteq J^{[p^e]} \Longleftrightarrow (I^n)^{[1/p^e]} \subseteq J
\end{equation*}
where $(I^n)^{[1/p^e]}$ denotes the $p^e$-th \emph{Frobenius root} of $I^n$, as defined in \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
The option {\tt ContainmentTest} for {\tt nu} allows the user to choose which of the two types of containment statements appearing above to use toward the calculation of $\nu_I^J(p^e)$.

@@

The option {\tt ContainmentTest} has a third possible value, {\tt FrobeniusPower}, which may produce a different result than the other two values.
Given an ideal $I$, the first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
When {\tt ContainmentTest} is set to {\tt FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function {\tt nu} computes the
maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.  This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not coincide in general.
For example, the two commands below give different output values.

@@

o4 = 8
\end{MyVerbatim}
}

\medspace
\noindent In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.

The last option we describe for {\tt nu} is {\tt IsLocal}.  When the value of {\tt IsLocal} is set to false (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead computes
\[
\min_{J \in \mathfrak{m}-\Spec R} (\nu_I^J(p^e))
\]
This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it computes for which $n$ we have $(I^n)^{[1/p^e]}$ is a unit ideal.

\medspace
{\small
\setstretch{.67}
\begin{MyVerbatim}
    i1 : R = ZZ/7[x,y];

>>>>

We now describe the options available for the function {\tt nu}.  We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when it is instead a polynomial $f$.

In general, the function {\tt nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
The user can specify how this search is approached through the  option {\tt Search}.  Namely, a binary search is used when {\tt Search} is set to {\tt Binary} (and this is the option's default value), and a linear search is run when it is set to {\tt Linear}.

@@

As described in the introduction, the integer $\nu_I^J(p^e)$ is defined in terms of containment conditions on powers of ideals.
For positive integers $n$ and $e$, and an ideal $I$ contained in the radical of another ideal $J$, we have that
\begin{equation*}
  I^n \subseteq J^{[p^e]} \Longleftrightarrow (I^n)^{[1/p^e]} \subseteq J
\end{equation*}
where $(I^n)^{[1/p^e]}$ denotes the $p^e$-th \emph{Frobenius root} of $I^n$, as defined in \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
The option {\tt ContainmentTest} for {\tt nu} allows the user to choose which of the two types of containment statements appearing above to use toward the calculation of $\nu_I^J(p^e)$.

@@

The option {\tt ContainmentTest} has a third possible value, {\tt FrobeniusPower}, which may produce a different result than the other two values.
Given an ideal $I$, the first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
When {\tt ContainmentTest} is set to {\tt FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function {\tt nu} computes the
maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.  This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not agree in general.
For example, the two commands below give different output values.

@@

o4 = 8
\end{MyVerbatim}
}
\medspace

\noindent In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.

The last option we describe for {\tt nu} is {\tt IsLocal}.  When the value of {\tt IsLocal} is set to {\tt false} (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead calculates
\[
\min_{J \in \mathfrak{m}-\Spec R} (\nu_I^J(p^e))
\]
% This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it 
by determining the values $n$ for which $(I^n)^{[1/p^e]}$ is a unit ideal.
